Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-18 article.tex
major article struc.

Now, imagine that I asked you to compute the energy surface of a given molecule; how would you carry out this task? You would execute an algorithm that produces a numerical value. In Scalar Quantum of Molecular Energies two techniques used to determine the energy surface for a hydrogen molecule are discussed which are: 1) The Variational Quantum Eigensolver (VQE) and 2) The Quantum Phase Estimation Algorithm (PEA) which constitutes of the ‘original algorithm for quantum chemistry’.

@@

\subsection{The Quantum Phase Estimation Algorithm (PEA)}
Similarly to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have a sufficient overlap with the ground state.

Similarly, to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have a sufficient overlap with the ground state. Once the state is prepared in our desired state, an approximation is applied to the operator. Consequently, the initial state is mapped onto a superposition state, a state that is made up of different vectors. After that, the state is acted on in turn inducing a phase on the system. Since the way in which the system evolves is controlled, it is now entangled with the initialised state. Next, we measure the phase obtained corresponding to each value of energy. The system as a result collapses to a single state with an associated probability. We repeat this algorithm for a higher number of ‘special’ qubits until the lowest eigenenergy is obtained, or more precisely the energy of the ground state.

@@

\section{Technical Boxes}
\section{VQE}
\section{PEA}
\section{Experimental realisation (SQUID)}
 \fbox{\begin{minipage}[c]{32em}%
The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of superconducting interference device or SQUID. It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are charge states, and the superposition of these charge states is tuned using microwave resonators. The Xmon qubit has a number of favourable features, which include easy fabrication, fast qubit control and long qubit coherence times.

>>>>

Now, imagine that I asked you to compute the energy surface of a given molecule; how would you carry out this task? You would execute an algorithm that produces a numerical value. In Scalar Quantum of Molecular Energies two techniques used to determine the energy surface for a hydrogen molecule are discussed as follows: 
\begin{itemize}
\item The Variational Quantum Eigensolver (VQE)
\item The Quantum Phase Estimation Algorithm (PEA)
\end{itemize}
which constitutes of the ‘original algorithm for quantum chemistry’.

@@

\subsection{The Quantum Phase Estimation Algorithm (PEA)}
Similarly, to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have a sufficient overlap with the ground state. Once the state is prepared in our desired state, an approximation is applied to the operator. Consequently, the initial state is mapped onto a superposition state of various qubits, which is called the ancilla qubits. After that, the state is acted on in turn inducing a phase on the system. Since the way in which the system evolves is controlled, it is now entangled with the initialised state. Next, we measure the phase obtained corresponding to each value of energy. The system as a result collapses to a single state with an associated probability. We repeat this algorithm for a higher number of ‘special’ qubits until the lowest eigenenergy is obtained, or more precisely the energy of the ground state.

\fbox{\begin{minipage}[c]{32em}%
 \centerline{\textbf{PEA}}
 The molecular energies can be obtained by the time evolution of molecular Hamiltonian, which is a unitary operator $U = e^{-iHt}$. We can first prepare an initial state that strongly overlaps the ground state of molecular hydrogen. As any state $\ket{\psi(t)}$ evolved by unitary $U$ can be represent by applying phase difference onto initial state $e^{-iEt}\ket{\psi(0)}$. Phase estimation algorithm (PEA) is used then to find this relative phase and convert it into energy. In order to preform PEA we need to prepare two parts of qubits. First n qubits of superposition state $\frac{\ket{0} + \ket{1}}{\sqrt 2}$, second, our initial state. Since we can evolve states by unity operator. By inputting both parts of qubits onto a multiple controlled-U gate, the eigenvalue of each unitary $U$ will transform to each one of qubits in first part.

Now let us recap Quantum Fourier Transformation, one transforms the tensor product of multiple states onto phase of some superposition states.
\begin{footnotesize}
\[
	\ket{j_{1} j_{2} \cdots j_{n}}\rightarrow \frac{\left(\ket{0}+e^{2 \pi i 0. j_{n}}\ket{1}\right)\left(\ket{0}+e^{2 \pi i 0. j_{n-1} j_{n}}\ket{1}\right) \cdots\left( \ket{0}+e^{2 \pi i 0. j_{1} j_{2} \cdots j_{n-1} j_{n} }\ket{1}\right)}{2^{\frac{n}{2}}}
\] 
\end{footnotesize}

\end{minipage}}

 \fbox{\begin{minipage}[c]{32em}%
 \centerline{\textbf{Experimental realisation (SQUID)}}
The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of superconducting interference device or SQUID. It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are charge states, and the superposition of these charge states is tuned using microwave resonators. The Xmon qubit has a number of favourable features, which include easy fabrication, fast qubit control and long qubit coherence times.

@@

\section{Technical Boxes}
\section{VQE}
\section{PEA}

\section{Experimental realisation (SQUID)}
